Performance Improvement of Chombo 4

### 2023-10-23 example/DomainDecomposition/EBINS/exec/_zhang/report/main.tex

We find that different processors/GPUs have different optimal $num$\_$smooth$ in terms of runtimes (Figure \ref{fig:Performance on CPU Nodes}, \ref{fig:Performance on GPU Nodes}).

\begin{figure}[H]
    \begin{subfigure}{0.92\textwidth}
        \includegraphics[width=\textwidth]{Performance on CPU Nodes.png}
        \caption{CPU Processors}
        \label{fig:Performance on CPU Nodes}
    \end{subfigure}
    \begin{subfigure}[b]{0.92\textwidth}
        \includegraphics[width=\textwidth]{Performance on GPU Nodes.png}
        \caption{GPUs}
        \label{fig:Performance on GPU Nodes}
    \end{subfigure}
    \caption{Performance of CPU Processors and GPUs under various $num$\_$smooth$}
\end{figure}

>>>>

We find that different processors/GPUs have different optimal $num$\_$smooth$ in terms of runtimes. Once the optimal $num$\_$smooth$ is exceeded, the runtimes increase monotonically.

For CPU runs without $use$\_$w$\_$cycle$, the optimal $num$\_$smooth$ is 8 for 1 processor (Figure \ref{fig:1 Proc without w Cycle}) and 16 for 8 (Figure \ref{fig:8 Procs without w Cycle}) and 27 processors (Figure \ref{fig:27 Procs without w Cycle}).

\begin{figure}[H]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{1 Proc without w Cycle.png}
        \caption{1 CPU Processor}
        \label{fig:1 Proc without w Cycle}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{8 Proc without w Cycle.png}
        \caption{8 CPU Processors}
        \label{fig:8 Procs without w Cycle}
    \end{subfigure}

    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{27 Proc without w Cycle.png}
        \caption{27 CPU Processors}
        \label{fig:27 Procs without w Cycle}
    \end{subfigure}

    \caption{Performance of 1, 8 and 27 CPU Processors without $use$\_$w$\_$cycle$ under various $num$\_$smooth$}
\end{figure}

For CPU runs with $use$\_$w$\_$cycle$, the optimal $num$\_$smooth$ is 4 for 1 (Figure \ref{fig:1 Proc with w Cycle}) and 8 processors (Figure \ref{fig:8 Procs with w Cycle}) and 8 for 27 processors (Figure \ref{fig:27 Procs with w Cycle}).

\begin{figure}[H]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{1 Proc with w Cycle.png}
        \caption{1 CPU Processor}
        \label{fig:1 Proc with w Cycle}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{8 Proc with w Cycle.png}
        \caption{8 CPU Processors}
        \label{fig:8 Procs with w Cycle}
    \end{subfigure}

    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{27 Proc with w Cycle.png}
        \caption{27 CPU Processors}
        \label{fig:27 Procs with w Cycle}
    \end{subfigure}

    \caption{Performance of 1, 8 and 27 CPU Processors with $use$\_$w$\_$cycle$ under various $num$\_$smooth$}
\end{figure}

For GPU runs without $use$\_$w$\_$cycle$, the optimal $num$\_$smooth$ is 16 for 1 GPU (Figure \ref{fig:1 GPU without w Cycle}) and 8 for 8 GPUs (Figure \ref{fig:8 GPUs without w Cycle}).

\begin{figure}[H]
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{1 GPU without w Cycle.png}
        \caption{1 GPU}
        \label{fig:1 GPU without w Cycle}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{8 GPUs without w Cycle.png}
        \caption{8 GPUs}
        \label{fig:8 GPUs without w Cycle}
    \end{subfigure}
    \caption{Performance of 1, 8 GPUs without $use$\_$w$\_$cycle$ under various $num$\_$smooth$}
\end{figure}

For GPU runs with $use$\_$w$\_$cycle$, the optimal $num$\_$smooth$ is 16 for 1 GPU (Figure \ref{fig:1 GPU with w Cycle}) and 16 for 8 GPUs (Figure \ref{fig:8 GPUs with w Cycle}).

\begin{figure}[H]
    \begin{subfigure}{0.48\textwidth}
        \includegraphics[width=\textwidth]{1 GPU with w Cycle.png}
        \caption{1 GPU}
        \label{fig:1 GPU with w Cycle}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{8 GPUs with w Cycle.png}
        \caption{8 GPUs}
        \label{fig:8 GPUs with w Cycle}
    \end{subfigure}
    \caption{Performance of 1, 8 GPUs with $use$\_$w$\_$cycle$ under various $num$\_$smooth$}
\end{figure}
